---
title: "Combined A2SF Analysis"
author: "viwa"
date: "2024-08-30"
output:
  html_document: default
  pdf_document: default
---

```{r echo=FALSE, message=FALSE, warning=FALSE, results="hide"}
library(knitr)
library(kableExtra)
library(BSDA)
library(tidyr)
library(reshape2)
library(dplyr)
library(webshot)
library(viridis)
library(purrr)
library(zipcodeR)
library(usdata)
library(ggplot2)
library(leaflet)
library(mapview)
library(htmlwidgets)
library(sf)
library(tidygeocoder)
library(lubridate)
library(tigris)
library(leaflet.extras)
library(htmlwidgets)
library(countries)
library(cities)
library(stringr)
library(rcompanion)
options(tigris_use_cache = TRUE, tigris_progress = FALSE)
```

```{r, echo=FALSE, warning= FALSE, message= FALSE}
in_season <- readxl::read_xlsx("In Season A2SF Survey data.xlsx")
post_season <- read.csv("post_season-processed.csv")
```

### Combining Survey Results

*Combine surveys into one data frame, with labels to group surveys by collection time frame.*

```{r, echo=FALSE, warning= FALSE, message= FALSE}
in_season <- in_season %>%
  filter(!is.na(`Respondent ID`)) %>%
  select(
    -c(Type, Referrer, Platform, Agent, ...51, ...52,...23,...25,...27,...29,...31,...33),
    -starts_with("Tag Name"),
    -starts_with("Tag Value"),
    -starts_with("IP")
  )

post_season <- post_season %>%
  filter(!is.na(Respondent.ID)) %>%
  select(-c(X, Type, Referrer, Platform, Agent,...47,...48,...23,...25,...27,...29,...31,...33),
    -starts_with("Tag.Name"),
    -starts_with("Tag.Value"),
    -starts_with("IP"))
```

```{r, echo=FALSE, warning= FALSE, message= FALSE}
post_season$What.is.your.zip.code. <- as.character(post_season$What.is.your.zip.code.)
```

```{r, echo=FALSE, warning= FALSE, message= FALSE}

in_season <- in_season %>%
  mutate(source = "In Season")

in_season <- in_season %>%
  rename(other.gender = ...11,
         other.race = ...14,
         other.attendance.factors = ...18,
         other.fav.offerings = ...20,
         )
  
post_season <- post_season %>%
  mutate(source = "Post Season")

post_season <- post_season %>%
  rename(other.gender = ...11,
         other.race = ...14,
         other.attendance.factors = ...18,
         other.fav.offerings = ...20,
         )
# clean_all <- bind_rows(in_season_data, post_season_data)
```

```{r, echo=FALSE, warning= FALSE, message= FALSE}
make_proper <- function(name) {
  name %>%
    str_replace_all("\\.", " ") %>%
    str_replace_all(" {2,}", " ") %>%
    str_replace_all("[[:punct:]]", "") %>%
    str_trim()
}

names(in_season) <- sapply(names(in_season), make_proper)

names(post_season) <- sapply(names(post_season), make_proper)
```

```{r, echo=FALSE, warning= FALSE, message= FALSE}
in_season <- in_season %>%
  rename(race_ethnicity = `Which of the following describes your race andor ethnicity Note we recognize the following list is not allencompassing for how people may identify Please select all that apply and in addition you may further selfdescribe race andor ethnicity using the Other option`,
         donation = `A2SF is an independent communitysupported 501c3 nonprofit organization with individual donors contributing $340000 or 20 of our yearly budget How likely are you to donate to our organization`,
         future_attend = `On a scale of 110 how likely are you to attend one of our events in the future`,
         recommend_family = `On a scale of 110 how likely are you to recommend our events to a friend or family member`,
         music_satisfaction = `On a scale of 110 how satisfied are you with the Top of the Park music programming`,
         kids_satisfaction = `On a scale of 110 how satisfied are you with family offerings KidZone Kids Rock at Top of the Park`,
         overall_trajectory = `On a scale of 110 how do you feel about the overall trajectory that A2SF is heading in`,
         gift_email = `If you would like to be entered to win a $50 gift card please provide your email address`)
```

```{r, echo=FALSE, warning= FALSE, message= FALSE}
post_season <- post_season %>%
  rename(race_ethnicity = `Which of the following describes your race and or ethnicity Note we recognize the following list is not all encompassing for how people may identify Please select all that apply and in addition you may further self describe race and or ethnicity using the Other option`,
         donation = `A2SF is an independent community supported 501 c 3 nonprofit organization with individual donors contributing 340 000 or 20 of our yearly budget How likely are you to donate to our organization`,
         future_attend = `On a scale of 1 10 how likely are you to attend one of our events in the future`,
         recommend_family = `On a scale of 1 10 how likely are you to recommend our events to a friend or family member`,
         music_satisfaction = `On a scale of 1 10 how satisfied are you with the Top of the Park music programming`,
         kids_satisfaction = `On a scale of 1 10 how satisfied are you with family offerings KidZone Kids Rock at Top of the Park`,
         overall_trajectory = `On a scale of 1 10 how do you feel about the overall trajectory that A2SF is heading in`,
         gift_email = `If you would like to be entered to win a 50 gift card please provide your email address`) %>%
  mutate(future_attend = as.character(future_attend)) %>%
  mutate(donation = as.character(donation)) %>%
  mutate(recommend_family = as.character(recommend_family)) %>%
  mutate(music_satisfaction = as.character(music_satisfaction)) %>%
  mutate(kids_satisfaction = as.character(kids_satisfaction)) %>%
  mutate(overall_trajectory = as.character(overall_trajectory))
```

```{r, echo=FALSE, warning= FALSE, message= FALSE}
clean_all <- bind_rows(in_season, post_season)
clean_all <- clean_all %>%
  select(`Respondent ID`,
         source,
         everything())
```

#### Where are visitors from?\

*Pie chart of all zip codes represented by respondents.*

```{r, echo=FALSE, warning= FALSE, message= FALSE}
clean_all <- clean_all %>%
  filter(nchar(`What is your zip code`) == 5)
```

```{r, echo=FALSE, warning= FALSE, message= FALSE}
all_zip_group_counts <- clean_all %>%
  select(`Respondent ID`,source,`What is your zip code`,State) %>%
  left_join(zip_code_db, by = c("What is your zip code" = "zipcode")) %>%
  mutate(state_abbr = state2abbr(State)) %>%
  select(source, `What is your zip code`, state_abbr, state) %>%
  filter(state_abbr == state) %>%
  group_by(`What is your zip code`) %>%
  summarise(count = n()) %>%
  mutate(grouped_zip = case_when(
    count == 1 ~ "Other",
    TRUE ~ `What is your zip code`
  ))
```

```{r, echo=FALSE, warning= FALSE, message= FALSE}
combined_zip_count_all <- all_zip_group_counts %>%
  group_by(grouped_zip, count) %>%
  summarise(count2 = n()) %>%
  ungroup() %>%
  mutate(combined = count*count2) %>%
  select(grouped_zip, combined)

adding_fractions <- combined_zip_count_all %>%
  mutate(
    fraction = combined / sum(combined),
    ymax = cumsum(fraction),
    ymin = c(0, head(ymax, n = -1)),
    labelPosition = (ymax + ymin) / 2
    )

ggplot(adding_fractions, aes(ymax = ymax, ymin = ymin, xmax = 4, xmin = 3, fill = grouped_zip)) +
  geom_rect(color="black") +
  geom_text(x = 4.2, aes(y = labelPosition, label = grouped_zip), size = 2) + # Position labels outside
  geom_segment(aes(x = 4, xend = 4, y = labelPosition, yend = labelPosition), color = "black") + # Add line from pie to label
  coord_polar(theta = "y") +
  ggtitle("Visitors by Zip Code") +
  scale_fill_brewer(palette = "Set3") +
  theme_void() +
  theme(legend.position = "none")
```

*All visitors, by county of origin. NOTE: numbers above bars represent the proportion of visitors from represented counties.*

```{r, echo=FALSE, warning= FALSE, message= FALSE}
all_zipcodeR <- reverse_zipcode(combined_zip_count_all$grouped_zip)


combined_zip_count_all %>%
  left_join(all_zipcodeR, by = c("grouped_zip" = "zipcode")) %>%
  group_by(county) %>%
  summarize(count = sum(combined)) %>%
  filter(!is.na(county)) %>%
  mutate(frac = round(count/sum(count),2)) %>%
  ggplot(aes(reorder(county, -count), count, fill = county)) + geom_bar(stat = "identity") + theme(axis.text.x = element_text(angle = 30, vjust = 0.7, hjust = 0.5)) + geom_text(aes(label = frac), vjust = -0.1, position = position_dodge(0.9), size = 2) + theme(legend.position = "none") + labs(y = "Number of Visitors", x = "County", title = "Visitors by County - All")
```


#### What ages are visitors?

*Bar graph of visitors by the survey source.*

Rationale: Differently-aged visitor groups may vary across collection method. Both surveys were administered online, but patrons were reached out in-person for in-season responses or online via email and social media for post-season responses. This can lead to variability that needs to be assessed.

```{r, echo=FALSE, warning= FALSE, message= FALSE}
desired_order <- c("Under 18 years", "18 to 24 years", "25 to 34 years", 
                   "35 to 44 years", "45 to 54 years", "55 to 64 years", 
                   "65 or older", "Decline to answer")
clean_all$`What is your age` <- factor(clean_all$`What is your age`, levels = desired_order, ordered = TRUE)

clean_all %>%
  group_by(source, `What is your age`) %>%
  summarise(count = n()) %>%
  mutate(frac = round(count/sum(count),2)) %>%
  ggplot(aes(x = `What is your age`, y = count, fill = source)) + geom_bar(stat = "identity", position = "dodge") + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + labs(x = "Age Group", y = "Count", title = "Grouped Respondents by Age and Survey Type") + geom_text(aes(label = frac), vjust = -0.1, position = position_dodge(0.9), size = 2)
```

*Is there a statistical difference between age-group demographics for in-season vs post-season respondents?*

Using the eye test, older age groups *seem* to answer more in the post-season, while younger groups were over-sampled in the in-season group. We need to verify this statistically using a chi-square test to demonstrate the response behaviors may vary between response groups. The Pearson's Chi-squared test indicates that there is a difference in respondents by age group between the two survey sources.

```{r, echo=FALSE, warning= FALSE, message= FALSE}
contingency_table <- table(clean_all$source, clean_all$`What is your age`)

chi_sq_result <- chisq.test(contingency_table)

print(chi_sq_result)
```

*Perform pairwise chi-squared tests and adjust the p-values using Bonferroni correction.*

Without adjustments, performing multiple pairwise tests increases the likelihood of finding at least one significant result purely by chance.

The Bonferroni correction adjusts the significance level for each individual test by dividing the desired overall significance level (e.g., 0.05) by the number of comparisons. This reduces the likelihood of Type I errors but may be conservative and reduce power.

If the overall chi-squared test (or another omnibus test) is significant, it indicates that not all groups are equal, prompting the need to find out where those differences lie.

```{r, echo=FALSE, warning= FALSE, message= FALSE}
pairwise_chi_sq_test <- function(contingency_table) {
  pairs <- combn(colnames(contingency_table), 2, simplify = FALSE)
  results <- lapply(pairs, function(pair) {
    sub_table <- contingency_table[, pair, drop = FALSE]
    test_result <- chisq.test(sub_table)
    data.frame(
      Group1 = pair[1],
      Group2 = pair[2],
      p.value = test_result$p.value
    )
  })
  results_df <- do.call(rbind, results)
  results_df$p.adjusted <- p.adjust(results_df$p.value, method = "bonferroni")
  return(results_df)
}

pairwise_results <- pairwise_chi_sq_test(contingency_table)

pairwise_matrix <- acast(pairwise_results, Group1 ~ Group2, value.var = "p.adjusted")

pairwise_matrix[lower.tri(pairwise_matrix)] <- t(pairwise_matrix)[lower.tri(pairwise_matrix)]

pairwise_long <- melt(pairwise_matrix, na.rm = TRUE)

ggplot(pairwise_long, aes(Var1, Var2, fill = value)) +
  geom_tile(color = "white") +
  scale_fill_gradient(low = "white", high = "lightblue", na.value = "white") +
  labs(x = 'Age Group', y = 'Age Group', fill = 'Adjusted P-value') +
  theme_minimal() + theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

#### Visitor gender demographics

*Bar graph of number of visitors by their self-identified gender.*

```{r, echo=FALSE, warning= FALSE, message= FALSE}
clean_all %>%
  group_by(source, `With what gender do you most identify`) %>%
  summarise(count = n()) %>%
  filter(`With what gender do you most identify` != "Prefer to self-describe, below") %>%
  mutate(frac = round(count/sum(count),2)) %>%
  ggplot(aes(x = reorder(`With what gender do you most identify`,-count), y = count, fill = source)) + geom_bar(stat = "identity", position = "dodge") + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + labs(x = "Gender Identity", y = "Count", title = "Grouped Respondents by Self-Identified Gender and Survey Type") + geom_text(aes(label = frac), vjust = -0.1, position = position_dodge(0.9), size = 2)
```

*Other self-described gender identities.*

```{r, echo=FALSE, warning= FALSE, message= FALSE}
clean_all %>%
  group_by(source, `other gender`) %>%
  summarize(count = n()) %>%
  filter(!is.na(`other gender`)) %>%
  kable(col.names = c("Survey", "Other Identity", "Count"))
```


#### Visitor Race/Ethnicity demographics

*All distinct race/ethnicity identities*

```{r, echo=FALSE, warning= FALSE, message= FALSE}
clean_all %>%
  distinct(race_ethnicity) %>%
  filter(!is.na(race_ethnicity)) %>%
  arrange(race_ethnicity) %>%
  kable(col.names = "Race/Ethnicity")
```
*Ethnicity question.*

```{r, echo=FALSE, warning= FALSE, message= FALSE}
ethnicity <- clean_all %>%
  mutate(ethnicity = case_when(
    grepl("Hispanic, Latino or Spanish origin", race_ethnicity) ~ "Hispanic, Latino or Spanish origin",
    TRUE ~ "NOT Hispanic, Latino or Spanish origin"
  )) %>%
  select(`Respondent ID`,race_ethnicity,ethnicity) %>%
  group_by(ethnicity) %>%
  summarise(count = n()) %>%
  mutate(percentage = round(count/sum(count)*100, 2)) 

ethnicity %>%
  kable(col.names = c("Ethnicity", "Count", "Percent (%)"))
```

*Bar graph of race/ethnicity identities, by survey, with mixed heritages collapsed into a single general category. Does not include Hispanic, Latino, or Spanish origin, as this is used to assess "ethnicity" separately, per US Census standards.*

```{r, echo=FALSE, warning= FALSE, message= FALSE}
clean_all %>%
  mutate(Collapsed = case_when(
    grepl("Hispanic, Latino or Spanish origin", race_ethnicity) & grepl(", ", race_ethnicity) ~ "Mixed heritage",
    grepl(", ", race_ethnicity) ~ "Mixed heritage",
    TRUE ~ race_ethnicity
  )) %>%
  group_by(source, Collapsed) %>%
  summarise(collapse_count = n()) %>%
  filter(!is.na(Collapsed)) %>%
  mutate(frac = round(collapse_count/sum(collapse_count),2)) %>%
  ggplot(aes(x = reorder(Collapsed,-collapse_count), y = collapse_count, fill = source)) + geom_bar(stat = "identity", position = "dodge") + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + labs(x = "Race/Ethnicity", y = "Count", title = " Respondents by Race/Ethnicity and Survey Type") + geom_text(aes(label = frac), vjust = -0.1, position = position_dodge(0.9), size = 2)

clean_all %>%
  mutate(Collapsed = case_when(
    grepl("Hispanic, Latino or Spanish origin", race_ethnicity) & grepl(", ", race_ethnicity) ~ "Mixed heritage",
    grepl(", ", race_ethnicity) ~ "Mixed heritage",
    TRUE ~ race_ethnicity
  )) %>%
  group_by(Collapsed) %>%
  summarise(collapse_count = n()) %>%
  filter(!is.na(Collapsed)) %>%
  mutate(frac = round(collapse_count/sum(collapse_count)*100,2)) %>%
  arrange(desc(collapse_count)) %>%
  kable(col.names = c("Race", "Frequency", "Percent (%)"))
  
```

*Is race/ethnicity breakdown different by source?*

The results suggest that although race/ethnicity comparisons with county demographics seem to be significantly different, the results are actually very similar between the two survey collection types and may suggest that the audience that A2SF reaches is represented appropriately.

```{r, echo=FALSE, warning= FALSE, message= FALSE}
contingency_table <- table(clean_all$source, clean_all$race_ethnicity)

chi_sq_result <- chisq.test(contingency_table)

print(chi_sq_result)
```

*Other race/ethnicity identities, as self-described by respondents.*

```{r, echo=FALSE, warning= FALSE, message= FALSE}
clean_all %>%
  group_by(source, `other race`) %>%
  summarize(count = n()) %>%
  filter(!is.na(`other race`)) %>%
  kable(col.names = c("Survey", "Other Identities", "Count"))
```

```{r, echo=FALSE, warning= FALSE, message= FALSE}
selections = c("Music at Top of the Park",
               "Movies by Moonlight",
               "Special Outdoor Attractions",
               "Retreat Classes on Power Center lawn",
               "Food Selections",
               "The Grove Beverage Garden",
               "KidZone",
               "Teen and Adult Activities",
               "I was invited to an event in the party tent",
               "Other _______________________")

selection_pattern <- paste0("\\b(", paste(selections, collapse = "|"), ")\\b")


clean_all_split <- clean_all %>%
  mutate(extractions = str_extract_all(`What are your favorite offerings tonight Choose up to three`, selection_pattern))

clean_all_split <- clean_all_split %>%
  mutate(extractions = map(extractions, ~c(.x, rep(NA, 3 - length(.x)))[1:3])) %>%
  unnest_wider(extractions, names_sep = "_")

clean_all_split <- clean_all_split %>%
  rename(fav_1 = extractions_1, fav_2 = extractions_2, fav_3 = extractions_3)

clean_all_split <- clean_all_split %>%
  select(`Respondent ID`, `Start Date`, `What are your favorite offerings tonight Choose up to three`, fav_1, fav_2, fav_3, `other fav offerings`
  ) %>%
  filter(!is.na(`Respondent ID`))
```

*All favorite offering counts by respondents.*

```{r, echo=FALSE, warning= FALSE, message= FALSE}
long_df <- clean_all_split %>%
  gather(key = "type", value = "offering", fav_1:fav_3, `other fav offerings`) %>%
  filter(!is.na(offering))

long_df %>%
  count(offering, sort = TRUE) %>%
  mutate(percent = round(n/sum(n)*100,2)) %>%
  kable(col.names = c("Offering", "Frequency", "Percent (%)"))
```

